|

### 2022-06-23 docs/rmd/paper.Rmd
autogit

@generalisation_in_gp criticizes that almost all applications published in the initial GP literature by @koza_main are not using separate training and testing data sets which might result in over fitting and a poor overall generalization ability of the programs that are produced. The author calls for a more widespread adoption of methods like generational sampling of new training cases or the overall separation into training and testing data sets to improve generalization in GP [@generalisation_in_gp, p.10].

An aspect that is suspected to negatively correlate with GP's generalization is overall size and in particular bloating of the resulting programs. Bloating can be described as a growth in the total size of a program that does not improve its performance in any meaningful way [@bloat_overfitting_gp, p. 1].
It has been widely suspected that GP configurations that produce very large programs also have a higher tendency to specialize on difficult or unusual test cases which could result in lower generalization [@wang_wagner_rondinelli_2019, p. 268]. The minimum description length principle (MDLP) describes this phenomenon by claiming that less complex models are more likely to perform better at generalizing than more complex models that achieve a comparable fitness during the training phase [@open_issues_gp, p. 349]. However MDLP should be considered with caution, experiments by @bloat_overfitting_gp on the prediction of bio availability for drugs demonstrate that GP based techniques can either bloat without over fitting or over fit without bloating [@bloat_overfitting_gp, p. 8].

@@

To further examine the difference in generalization behavior, the mean testing and training errors over each generation will be visualized for both algorithms. The specific aim of this visualization is to explore the mechanism of over fitting and to examine if differences between both methods can be detected.

@@

Some interesting observation from tables 6 and 7 can be made by comparing the mean of the variables $min\_training\_error$ and $testing\_error$. Variable $min\_training\_error$ represents the fitness, measured by the MSE, of the best performing solution that has been found during a single run of the experiment while the variable $testing\_error$ represents the fitness of the same solution if evaluated for the unknown fitness cases inside the testing data set. Tournament selection based GP achieves a mean $min\_training\_error$ of $16.483$ and a mean $testing\_error$ of $16.905$ while the GP system using $\epsilon$-lexicase selection can only achieve a mean $min\_training\_error$ of $22.013$ and a mean $testing\_error$ of $22.456$. These results indicate an overall performance benefit for tournament selection based GP in the experiment. It should also be mentioned that the best performing model over all 50 runs, measured by the minimum of variables $min\_training\_error$ and $testing\_error$, has been achieved by tournament selection with an MSE of 7.066 for the training data and	7.847 for the testing data.

If we compare the differences of $min\_training\_error$ and $testing\_error$ on the basis of each algorithm, we can observe that both tournament and $\epsilon$-lexicase achieve a slightly lower error on the training data than on the testing data. If we compute the total difference between the means of $min\_training\_error$ and $testing\_error$ for both algorithms tournament selection amounts to 0.422 and $\epsilon$-lexicase selection to 0.443. Regarding our primary research question, the differences in generalization, the initial observations do not seem to indicate a significant difference in the the relative gap between the solutions performance on testing data and training data.

@@

2. The differences in mean fitness between $min\_training\_error$ and $testing\_error$ are not statistically significant for both selection algorithms. If comparing the mean training error to the mean testing error, the p-values only computes to 0.309 for tournament selection and to 0.257 for $\epsilon$-lexicase selection. These findings fail to reject $H0_{2}$, based on the obtained results we can not find evidence that both algorithms demonstrate a significantly different performance between the training data and the previously unseen testing data.

To further examine the generalization behavior of both selection operators I plotted the mean fitness scores for both algorithms over the total number of 100 generations in figure 2. Figure 2 shows that both algorithms show little visual evidence of over fitting which would result in a growing gap between between $min\_training\_error$ and $testing\_error$ in the final stages of the evolutionary optimization. For $\epsilon$-lexicase selection a small gap can be observed starting at around the 90.th generation, while the minimum training error slowly converges a small increase in the testing error can be observed. Based on the limited amount of collected data, it is questionable if this small sign of over fitting can be interpreted as a weak indicator for an inferior generalization behavior of $\epsilon$-lexicase in comparison to tournament selection.

@@

Both subplots display a very similar behavior that is common for GP, we observe a strong trend for solutions to grow in size with each additional generation that is concluded. Another observation  that can be made is that the best solutions of each generation almost always have a larger size than the population average. On first impression, the differences between both selection operators appears to be insignificant. Again, I conducted a MWU test to test for statistical differences in the underlying distribution of sizes measured during the experiment.

@@

None of the differences in mean size are statistically significant. Again, based on the results obtained in my experiment, the evidence produced fails to reject the null hypothesis $H0_{3}$ that selection has no significant effect on differences in program size. It should be noted that the configuration of both GP algorithm did include two mechanisms that place limitations on the growth behavior of the individual solutions to avoid excessive bloating (see sub section 3.2.4).

@@

The objective of this research project has been to answer the question if the choice between two commonly used parent selection operators, tournament selection and $\epsilon$-lexicase selection, significantly influences the generalization behavior of GP for symbolic regression tasks.

The results obtained from my experiment did not demonstrate any statistically significant differences in generalization, both GP systems achieve a slightly lower mean error if evaluated for the training data sets than if evaluated for the unseen fitness cases of the testing data set. The mean differences between testing and training errors did not show statistical significance differences for both algorithms (summarized in table 9).

To further explore differences in generalization behavior the mean for both algorithms training and testing error over all generations for all 50 independent runs was visualized and analyzed (see figure 2). A very small and probably insignificant gap did show for $\epsilon$-lexicase selection in the final phase of the evolutionary search, in the grand scheme of things this approach also did not yield any clear evidence of differences in generalization.

A final attempt to explore possible differences between both GP systems has been to explore differences in growth behavior as an indicator for generalization. This idea was based on the wide spread hypothesis that increases in overall program size might be an indication of over fitting to the training data, the concept has been discussed in sub section 2.2. Again, based on my results I could not find statistically significant differences in the growth behavior between both selection operators.

An interesting finding of my analysis is, that the overall performance of tournament selection has shown to be significantly better than that of $\epsilon$-lexicase selection for the selected symbolic regression problem. This finding was rather unexpected based on the research of @epsilon_lexicase_main and @https://doi.org/10.48550/arxiv.1709.05394 that primarily inspired this research project in the first place.

>>>>

@generalisation_in_gp criticizes that almost all applications published in the initial GP literature by @koza_main are not using separate training and testing data sets which might result in overfitting and a poor overall generalization ability of the programs that are produced. The author calls for a more widespread adoption of methods like generational sampling of new training cases or the overall separation into training and testing data sets to improve generalization in GP [@generalisation_in_gp, p.10].

An aspect that is suspected to negatively correlate with GP's generalization is overall size and in particular bloating of the resulting programs. Bloating can be described as a growth in the total size of a program that does not improve its performance in any meaningful way [@bloat_overfitting_gp, p. 1].
It has been widely suspected that GP configurations that produce very large programs also have a higher tendency to specialize on difficult or unusual test cases which could result in lower generalization [@wang_wagner_rondinelli_2019, p. 268]. The minimum description length principle (MDLP) describes this phenomenon by claiming that less complex models are more likely to perform better at generalizing than more complex models that achieve a comparable fitness during the training phase [@open_issues_gp, p. 349]. However MDLP should be considered with caution, experiments by @bloat_overfitting_gp on the prediction of bio availability for drugs demonstrate that GP based techniques can either bloat without overfitting or over fit without bloating [@bloat_overfitting_gp, p. 8].

@@

To further examine the difference in generalization behavior, the mean testing and training errors over each generation will be visualized for both algorithms. The specific aim of this visualization is to explore the mechanism of overfitting and to examine if differences between both methods can be detected.

@@

A few interesting observations from tables 6 and 7 can be made by comparing the mean of the variables $min\_training\_error$ and $testing\_error$. Variable $min\_training\_error$ represents the fitness, measured by the MSE, of the best performing solution that has been found during a single run of the experiment. The variable $testing\_error$ represents the fitness of the same solution if evaluated for the unknown fitness cases inside the testing data set. Tournament selection based GP achieves a mean $min\_training\_error$ of $16.483$ and a mean $testing\_error$ of $16.905$ while the GP system using $\epsilon$-lexicase selection can only achieve a mean $min\_training\_error$ of $22.013$ and a mean $testing\_error$ of $22.456$. These results indicate an overall performance benefit for the tournament selection based GP in the experiment. It should also be mentioned that the best performing model over all 50 runs, measured by the minimum of variables $min\_training\_error$ and $testing\_error$, has been achieved by tournament selection with an MSE of 7.066 for the training data and	7.847 for the testing data.

If we compare the differences of $min\_training\_error$ and $testing\_error$ on the basis of each algorithm, we can observe that both tournament and $\epsilon$-lexicase achieve a slightly lower fitness on the training data than on the testing data. We compute the total difference between the means of $min\_training\_error$ and $testing\_error$ for both algorithms tournament selection amounts to 0.422 and $\epsilon$-lexicase selection to 0.443. The initial observations do not seem to indicate a significant difference in the the relative gap between the solutions' performance on testing data and training data.

@@

2. The differences in mean fitness between $min\_training\_error$ and $testing\_error$ are not statistically significant for neither selection algorithms. When comparing the mean training error to the mean testing error, the p-values only compute to 0.309 for tournament selection and to 0.257 for $\epsilon$-lexicase selection. These findings fail to reject $H0_{2}$, based on the obtained results we can not find evidence that both algorithms demonstrate a significantly different performance between the training data and the previously unseen testing data.

To further examine the generalization behavior of both selection operators I plotted the mean fitness scores for both algorithms over the total number of 100 generations in figure 2. Figure 2 shows that both algorithms show little visual evidence of overfitting which would result in a growing gap between between $min\_training\_error$ and $testing\_error$ in the final stages of the evolutionary optimization. For $\epsilon$-lexicase selection a small gap can be observed starting approximately at the 90th generation, while the minimum training error slowly converges a small increase in the testing error. Based on the limited amount of collected data, it is questionable if this small sign of overfitting can be interpreted as a weak indicator for an inferior generalization behavior of $\epsilon$-lexicase in comparison to tournament selection.

@@

Both subplots display a very similar behavior that is common for GP. We observe a strong trend for solutions to grow in size with each additional generation that is concluded. Another observation  that can be made is that the best solutions of each generation almost always have a larger size than the population average. On first impression, the differences between both selection operators appear to be insignificant. Again, I conducted a MWU test to examine statistical differences in the underlying distribution of sizes measured during the experiment.

@@

None of the differences in mean size are statistically significant. Again, based on the results obtained in my experiment, the evidence produced fails to reject the null hypothesis $H0_{3}$ that selection has no significant effect on differences in program size. It should be noted that the configuration of both GP algorithms did include two mechanisms that place limitations on the growth behavior of the individual solutions to avoid excessive bloating (see sub section 3.2.4).

@@

The objective of this research project is to answer the question if the choice between two commonly used parent selection operators, tournament selection and $\epsilon$-lexicase selection, significantly influences the generalization behavior of GP for symbolic regression tasks.

The results obtained from my experiment do not demonstrate any statistically significant differences in generalization. Both GP systems achieve a slightly lower mean error if evaluated for the training data sets than if evaluated for the unseen fitness cases of the testing data set. The mean differences between testing and training errors do not show statistically significant differences for neither algorithms (summarized in table 9).

To further explore differences in generalization behavior the mean for both algorithms training and testing error over all generations for all 50 independent runs is visualized and analyzed (see figure 2). A very small and probably insignificant gap does show for $\epsilon$-lexicase selection in the final phase of the evolutionary search. Comprehensively, this approach also does not yield any clear evidence of differences in generalization.

A final attempt to explore possible differences between both GP systems is to explore differences in growth behavior as an indicator for generalization. This idea is based on the wide spread hypothesis that increases in overall program size might be an indication of overfitting to the training data. This concept has been discussed in sub section 2.2. The results do not show statistically significant differences in the growth behavior between both selection operators.

An interesting finding of this analysis is, that the overall performance of tournament selection shows to be notably higher than the performance of $\epsilon$-lexicase selection for the selected symbolic regression problem. This finding is rather unexpected based on the research of @epsilon_lexicase_main and @https://doi.org/10.48550/arxiv.1709.05394 that is the primary source of inspiration for this research project.

### 2022-06-23 docs/rmd/paper.tex
autogit

Kushchu (2002) criticizes that almost all applications published in the
initial GP literature by Koza (1992) are not using separate training and
testing data sets which might result in over fitting and a poor overall
generalization ability of the programs that are produced. The author
calls for a more widespread adoption of methods like generational
sampling of new training cases or the overall separation into training
and testing data sets to improve generalization in GP (Kushchu, 2002, p.
10).

An aspect that is suspected to negatively correlate with GP's
generalization is overall size and in particular bloating of the
resulting programs. Bloating can be described as a growth in the total
size of a program that does not improve its performance in any
meaningful way (Silva and Vanneschi, 2009, p. 1). It has been widely
suspected that GP configurations that produce very large programs also
have a higher tendency to specialize on difficult or unusual test cases
which could result in lower generalization (Wang, Wagner and Rondinelli,
2019, p. 268). The minimum description length principle (MDLP) describes
this phenomenon by claiming that less complex models are more likely to
perform better at generalizing than more complex models that achieve a
comparable fitness during the training phase (O'Neill \emph{et al.},
2010, p. 349). However MDLP should be considered with caution,
experiments by Silva and Vanneschi (2009) on the prediction of bio
availability for drugs demonstrate that GP based techniques can either
bloat without over fitting or over fit without bloating (Silva and
Vanneschi, 2009, p. 8).

@@

Some interesting observation from tables 6 and 7 can be made by
comparing the mean of the variables \(min\_training\_error\) and
\(testing\_error\). Variable \(min\_training\_error\) represents the
fitness, measured by the MSE, of the best performing solution that has
been found during a single run of the experiment while the variable
\(testing\_error\) represents the fitness of the same solution if
evaluated for the unknown fitness cases inside the testing data set.
Tournament selection based GP achieves a mean \(min\_training\_error\)
of \(16.483\) and a mean \(testing\_error\) of \(16.905\) while the GP
system using \(\epsilon\)-lexicase selection can only achieve a mean
\(min\_training\_error\) of \(22.013\) and a mean \(testing\_error\) of
\(22.456\). These results indicate an overall performance benefit for
tournament selection based GP in the experiment. It should also be
mentioned that the best performing model over all 50 runs, measured by
the minimum of variables \(min\_training\_error\) and
\(testing\_error\), has been achieved by tournament selection with an
MSE of 7.066 for the training data and 7.847 for the testing data.

If we compare the differences of \(min\_training\_error\) and
\(testing\_error\) on the basis of each algorithm, we can observe that
both tournament and \(\epsilon\)-lexicase achieve a slightly lower error
on the training data than on the testing data. If we compute the total
difference between the means of \(min\_training\_error\) and
\(testing\_error\) for both algorithms tournament selection amounts to
0.422 and \(\epsilon\)-lexicase selection to 0.443. Regarding our
primary research question, the differences in generalization, the
initial observations do not seem to indicate a significant difference in
the the relative gap between the solutions performance on testing data
and training data.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The differences in mean fitness between tournament selection and
  \(\epsilon\)-lexicase selection are highly statistical significant
  even if considering an \(\alpha\) of 0.01. For the given symbolic
  regression task tournament selection achieves a better mean
  performance on both the training as well as the testing data set than
  \(\epsilon\)-lexicase selection. These findings contradict the
  hypothesis \(H0_{1}\) described in subsection 3.1 and are contrary to
  some of the research that was summarized in subsections 2.1 and
  2.3.(La Cava, Spector and Danai, 2016) (La Cava \emph{et al.}, 2017).
\item
  The differences in mean fitness between \(min\_training\_error\) and
  \(testing\_error\) are not statistically significant for both
  selection algorithms. If comparing the mean training error to the mean
  testing error, the p-values only computes to 0.309 for tournament
  selection and to 0.257 for \(\epsilon\)-lexicase selection. These
  findings fail to reject \(H0_{2}\), based on the obtained results we
  can not find evidence that both algorithms demonstrate a significantly
  different performance between the training data and the previously
  unseen testing data.
\end{enumerate}

To further examine the generalization behavior of both selection
operators I plotted the mean fitness scores for both algorithms over the
total number of 100 generations in figure 2. Figure 2 shows that both
algorithms show little visual evidence of over fitting which would
result in a growing gap between between \(min\_training\_error\) and
\(testing\_error\) in the final stages of the evolutionary optimization.
For \(\epsilon\)-lexicase selection a small gap can be observed starting
at around the 90.th generation, while the minimum training error slowly
converges a small increase in the testing error can be observed. Based
on the limited amount of collected data, it is questionable if this
small sign of over fitting can be interpreted as a weak indicator for an
inferior generalization behavior of \(\epsilon\)-lexicase in comparison
to tournament selection.

@@

None of the differences in mean size are statistically significant.
Again, based on the results obtained in my experiment, the evidence
produced fails to reject the null hypothesis \(H0_{3}\) that selection
has no significant effect on differences in program size. It should be
noted that the configuration of both GP algorithm did include two
mechanisms that place limitations on the growth behavior of the
individual solutions to avoid excessive bloating (see sub section
3.2.4).

@@

The objective of this research project has been to answer the question
if the choice between two commonly used parent selection operators,
tournament selection and \(\epsilon\)-lexicase selection, significantly
influences the generalization behavior of GP for symbolic regression
tasks.

The results obtained from my experiment did not demonstrate any
statistically significant differences in generalization, both GP systems
achieve a slightly lower mean error if evaluated for the training data
sets than if evaluated for the unseen fitness cases of the testing data
set. The mean differences between testing and training errors did not
show statistical significance differences for both algorithms
(summarized in table 9).

To further explore differences in generalization behavior the mean for
both algorithms training and testing error over all generations for all
50 independent runs was visualized and analyzed (see figure 2). A very
small and probably insignificant gap did show for \(\epsilon\)-lexicase
selection in the final phase of the evolutionary search, in the grand
scheme of things this approach also did not yield any clear evidence of
differences in generalization.

A final attempt to explore possible differences between both GP systems
has been to explore differences in growth behavior as an indicator for
generalization. This idea was based on the wide spread hypothesis that
increases in overall program size might be an indication of over fitting
to the training data, the concept has been discussed in sub section 2.2.
Again, based on my results I could not find statistically significant
differences in the growth behavior between both selection operators.

An interesting finding of my analysis is, that the overall performance
of tournament selection has shown to be significantly better than that
of \(\epsilon\)-lexicase selection for the selected symbolic regression
problem. This finding was rather unexpected based on the research of La
Cava, Spector and Danai (2016) and La Cava \emph{et al.} (2017) that
primarily inspired this research project in the first place.

>>>>

Kushchu (2002) criticizes that almost all applications published in the
initial GP literature by Koza (1992) are not using separate training and
testing data sets which might result in overfitting and a poor overall
generalization ability of the programs that are produced. The author
calls for a more widespread adoption of methods like generational
sampling of new training cases or the overall separation into training
and testing data sets to improve generalization in GP (Kushchu, 2002, p.
10).

An aspect that is suspected to negatively correlate with GP's
generalization is overall size and in particular bloating of the
resulting programs. Bloating can be described as a growth in the total
size of a program that does not improve its performance in any
meaningful way (Silva and Vanneschi, 2009, p. 1). It has been widely
suspected that GP configurations that produce very large programs also
have a higher tendency to specialize on difficult or unusual test cases
which could result in lower generalization (Wang, Wagner and Rondinelli,
2019, p. 268). The minimum description length principle (MDLP) describes
this phenomenon by claiming that less complex models are more likely to
perform better at generalizing than more complex models that achieve a
comparable fitness during the training phase (O'Neill \emph{et al.},
2010, p. 349). However MDLP should be considered with caution,
experiments by Silva and Vanneschi (2009) on the prediction of bio
availability for drugs demonstrate that GP based techniques can either
bloat without overfitting or over fit without bloating (Silva and
Vanneschi, 2009, p. 8).

@@

A few interesting observations from tables 6 and 7 can be made by
comparing the mean of the variables \(min\_training\_error\) and
\(testing\_error\). Variable \(min\_training\_error\) represents the
fitness, measured by the MSE, of the best performing solution that has
been found during a single run of the experiment. The variable
\(testing\_error\) represents the fitness of the same solution if
evaluated for the unknown fitness cases inside the testing data set.
Tournament selection based GP achieves a mean \(min\_training\_error\)
of \(16.483\) and a mean \(testing\_error\) of \(16.905\) while the GP
system using \(\epsilon\)-lexicase selection can only achieve a mean
\(min\_training\_error\) of \(22.013\) and a mean \(testing\_error\) of
\(22.456\). These results indicate an overall performance benefit for
the tournament selection based GP in the experiment. It should also be
mentioned that the best performing model over all 50 runs, measured by
the minimum of variables \(min\_training\_error\) and
\(testing\_error\), has been achieved by tournament selection with an
MSE of 7.066 for the training data and 7.847 for the testing data.

If we compare the differences of \(min\_training\_error\) and
\(testing\_error\) on the basis of each algorithm, we can observe that
both tournament and \(\epsilon\)-lexicase achieve a slightly lower
fitness on the training data than on the testing data. We compute the
total difference between the means of \(min\_training\_error\) and
\(testing\_error\) for both algorithms tournament selection amounts to
0.422 and \(\epsilon\)-lexicase selection to 0.443. The initial
observations do not seem to indicate a significant difference in the the
relative gap between the solutions' performance on testing data and
training data.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The differences in mean fitness between tournament selection and
  \(\epsilon\)-lexicase selection are highly statistical significant
  even if considering an \(\alpha\) of 0.01. For the given symbolic
  regression task tournament selection achieves a better mean
  performance on both the training as well as the testing data set than
  \(\epsilon\)-lexicase selection. These findings contradict the
  hypothesis \(H0_{1}\) described in subsection 3.1 and are contrary to
  some of the research that was summarized in subsections 2.1 and
  2.3.(La Cava, Spector and Danai, 2016) (La Cava \emph{et al.}, 2017).
\item
  The differences in mean fitness between \(min\_training\_error\) and
  \(testing\_error\) are not statistically significant for neither
  selection algorithms. When comparing the mean training error to the
  mean testing error, the p-values only compute to 0.309 for tournament
  selection and to 0.257 for \(\epsilon\)-lexicase selection. These
  findings fail to reject \(H0_{2}\), based on the obtained results we
  can not find evidence that both algorithms demonstrate a significantly
  different performance between the training data and the previously
  unseen testing data.
\end{enumerate}

To further examine the generalization behavior of both selection
operators I plotted the mean fitness scores for both algorithms over the
total number of 100 generations in figure 2. Figure 2 shows that both
algorithms show little visual evidence of overfitting which would result
in a growing gap between between \(min\_training\_error\) and
\(testing\_error\) in the final stages of the evolutionary optimization.
For \(\epsilon\)-lexicase selection a small gap can be observed starting
approximately at the 90th generation, while the minimum training error
slowly converges a small increase in the testing error. Based on the
limited amount of collected data, it is questionable if this small sign
of overfitting can be interpreted as a weak indicator for an inferior
generalization behavior of \(\epsilon\)-lexicase in comparison to
tournament selection.

@@

None of the differences in mean size are statistically significant.
Again, based on the results obtained in my experiment, the evidence
produced fails to reject the null hypothesis \(H0_{3}\) that selection
has no significant effect on differences in program size. It should be
noted that the configuration of both GP algorithms did include two
mechanisms that place limitations on the growth behavior of the
individual solutions to avoid excessive bloating (see sub section
3.2.4).

@@

The objective of this research project is to answer the question if the
choice between two commonly used parent selection operators, tournament
selection and \(\epsilon\)-lexicase selection, significantly influences
the generalization behavior of GP for symbolic regression tasks.

The results obtained from my experiment do not demonstrate any
statistically significant differences in generalization. Both GP systems
achieve a slightly lower mean error if evaluated for the training data
sets than if evaluated for the unseen fitness cases of the testing data
set. The mean differences between testing and training errors do not
show statistically significant differences for neither algorithms
(summarized in table 9).

To further explore differences in generalization behavior the mean for
both algorithms training and testing error over all generations for all
50 independent runs is visualized and analyzed (see figure 2). A very
small and probably insignificant gap does show for \(\epsilon\)-lexicase
selection in the final phase of the evolutionary search.
Comprehensively, this approach also does not yield any clear evidence of
differences in generalization.

A final attempt to explore possible differences between both GP systems
is to explore differences in growth behavior as an indicator for
generalization. This idea is based on the wide spread hypothesis that
increases in overall program size might be an indication of overfitting
to the training data. This concept has been discussed in sub section
2.2. The results do not show statistically significant differences in
the growth behavior between both selection operators.

An interesting finding of this analysis is, that the overall performance
of tournament selection shows to be notably higher than the performance
of \(\epsilon\)-lexicase selection for the selected symbolic regression
problem. This finding is rather unexpected based on the research of La
Cava, Spector and Danai (2016) and La Cava \emph{et al.} (2017) that is
the primary source of inspiration for this research project.
